---
title: "Life Expectancy"
author: "Matthew Campbell"
date: "1/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

[Life expectancy data](https://catalog.data.gov/dataset/age-adjusted-death-rates-and-life-expectancy-at-birth-all-races-both-sexes-united-sta-1900) was downloaded from data.gov. This dataset contains death rates and life-expectancy statistics from 1900 to 2015. Exploratory analysis was conducted on this dataset.

```{r get_data}

source("process_data.R")

summary(expectancy)

```

## Expectancy Dataset Sample

Below you will find a widget that you may use to few the contents of the data expectancy dataset. This is the dataset that will be explored later on in this analysis.

```{r}

library(DT)

datatable(expectancy, 
          options = list(pageLength = 5))

```

## Life Expectancy Plot

The plot below shows life expectancy by year for all sexes.

```{r echo=FALSE, message=FALSE}

library(plotly)

i_plot <- 
  expectancy %>% 
  filter(race == "All Races") %>% 
  ggplot(aes(year, life_expectancy)) +
  geom_line(aes(color = sex))

ggplotly(i_plot)

```

As you can see, life expectancy rises for everyone from 1900 to 2015. Women have a higher life expectancy than men and both groups follow the same upward trend while maintaining a difference between the two groups.
